Poseidon Adventure

### 2020-05-22 docs/index.Rmd
add to index
correct link
update index visualization date
update nobacod html

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, started March 18, 2020</a>

@@

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, updated May 22, 2020</a>

@@

### Visualize functions for documentation

<a href="https://sgaichas.github.io/poseidon-dev/Visualize_atlantisom.html" target="_blank">Different packages to visualize `atlantisom` functions, updated May 21, 2020</a>
